### 2015-09-10 fundamentals/impl.tex
fixes misformatted quotes

\begin{itemize}
    \item "manual" (currently implemented) is the default mode
        where agents decay materials when requested by an archetype,
    \item "never" (currently implemented) globally turns off all decay.
        The Material decay function does nothing,
    \item "lazy" (currently implemented) decays material automatically whenever
         its composition is observed (e.g. when an agent queries information
         about a material's $^{239}$Pu content),
    \item "periodic" (future) automatically decays all materials in a
        simulation with some fixed frequency.
\end{itemize}

@@

\Gls{CI} is the idea that software should be tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  Under \gls{CI}, every pull request is automatically
tested independently, immediately as it is proposed. The results of this
testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
project currently uses the CircleCI \cite{circleci} service for continuous integration.
Whenever a pull request is created, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the
problems.

>>>>

\begin{itemize}
    \item ``manual'' (currently implemented) is the default mode
        where agents decay materials when requested by an archetype,
    \item ``never'' (currently implemented) globally turns off all decay.
        The Material decay function does nothing,
    \item ``lazy'' (currently implemented) decays material automatically whenever
         its composition is observed (e.g. when an agent queries information
         about a material's $^{239}$Pu content),
    \item ``periodic'' (future) automatically decays all materials in a
        simulation with some fixed frequency.
\end{itemize}

@@

\Gls{CI} is the idea that software should be tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  Under \gls{CI}, every pull request is automatically
tested independently, immediately as it is proposed. The results of this
testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
Whenever a pull request is created, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the
problems.
